%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Anton Zavyalov} % Your name
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{+7 960 956 61 14 \\ megadeathlightsaber@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Polzunov Altai State Technical University, Barnaul} \hfill {\em 2017 - 2021} 
\\ Bachelor
\\09.03.04 - Software Engineering\\
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\begin{rSection}{Programming background}
I have been programming since I was 11. At first I was interested in modding and game development, so my first programming languages were Lua, C\# and Haxe (Google it, it's awesome!).

From the first year in university I am interested in the theory of programming languages and functional programming. I am familiar with such languages as Scheme, Haskell, OCaml and others. Obviously, my main interests are system programming and programming language design. My experience in programming language development includes a simple LISP interpreter with nested scope and higher order functions; an interpreter of a C-like language  and LLVM-powered compiler for it.

My interests do not contradict the fact that I am open to any interesting job offers. A big bonus if the offer is related to functional programming and programming language theory. ;)
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Flovver}
Visual functional programming language and rapid application development environment. Subject of my bachelor thesis in Polzunov Altai State Technical University.
\\
URL: \url{https://github.com/flovver}
    
{\bf evply - Graphical LISP Interpreter}
The goal of this project is to make symbolic computations more symbolic. You have a workspace where you can place and move primitives: numbers, lines, images, functions, etc. You select these primitives, click the button on the toolbar - and the selected objects are grouped into a symbolic expression.
A prototype of evply was developed for Hackathon Barnaul 2019.
\\
URL: \url{https://github.com/hackathonbrn/evply}

{\bf Daria}
Toy programming language with naive pattern matching design and implementation.
\\
URL: \url{https://github.com/andiogenes/daria}

{\bf TinyViz}
TinyViz is CLI graph visualization tool that was intended to help me with assignments for algorithms course. It supports hot reload! \\
URL: \url{https://github.com/andiogenes/TinyViz}
\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Computer Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages \ & Scala, Kotlin, Java, Go, C++, Python \\
Software \& Tools & Linux, Git, Docker \\
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}

\item \begin{rSubsection}{Stackeer.io}{December 2019 - April 2020}{Backend Developer}{}
The project was an ML-based system recommending reviewers for PRs from among the contributors.
\item Implemented a number of microservices in Go. Microservices are connected by REST and gRPC and
are managed by an orchestration system.
\item Created a command line tool to fetch data about repositories with GitHub GraphQLv4.
\item Refactored a legacy library consisting of one class with a large number of methods and fields. To do this, I wrote an ad-hoc tool that traverses an AST and emits a call graph. Next, this graph is rendered through GraphViz and I can see how to perform refactoring.
\end{rSubsection}

\item \begin{rSubsection}{Excelsior@Huawei}{July 2020 - Present}{Assistant Engineer}{}
NDA ;)
\end{rSubsection}


\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Academic Achievements} 
\item Participated in ICPC 2019-2020, NERC - Northern Eurasia Finals. Siberian and Far-Eastern Site. Our team took 16th place out of 49 (\textbf{in the regional standings}).
\end{rSection}

\newpage

%----------------------------------------------------------------------------------------
% Extra Curricular
%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Cirrucular} \itemsep -3pt
\item Was given a special award (Bitcoin-shaped chocolate bar) at Hackathon Barnaul 2019.
\item Played bass in a post-metal band called \href{https://sunhurt.bandcamp.com/}{Sunhurt} in 2019.
\item Linux ricing enthusiast (Check my current config at \href{https://github.com/andiogenes/dotfiles}{GitHub}).

\end{rSection}

\begin{rSection}{Personal Traits}
\item Highly motivated and eager to learn new things.
\item Ability to work as an individual as well as in group.
\end{rSection}
\end{document}
